---
title: "Exploring Melbourne business establishments"
output: github_document
---


```{r load libraries, include=FALSE}
library(here)
library(pacman)
p_load(ggplot2
       , janitor
       , magrittr
       , quanteda
       , tidyverse
       )
```

## Labelled data

This data associates a trading name with an ANZIC, and is collected as part of the City of Melbourne's Census of Land Use and Employment (CLUE) for the period 2002-2018.

```{r read in labelled data , include=FALSE}
# read in data
data_tr = read.csv(here("data","raw","Business_establishments__with_trading_name_and_industry_classification.csv"))
```

Here is a sample of the data from the Melbourne business survey:
```{r top 5 rows}
data_tr %>% as_tibble %>% head(5)
```

Close to 20K businesses are surveyed a year.
```{r}
data_tr %>% group_by(Census.year) %>% tally %>% arrange(-Census.year)
```

Inspecting a few businesses we can see a number of businesses were surveyed multiple times (over time or across many sites). There's also a large proportion of `Vacant` or `vacant` properties.
```{r}
data_tr %>% group_by(Trading.name) %>% tally %>% arrange(-n) %>% head(5)
```

Bigger organisations with with multiple sites can have different ANZSICs depending on what type of business they run on the site.
```{r}
data_tr %>% filter(Trading.name == "The University of Melbourne") %>% group_by(Industry..ANZSIC4..code, Industry..ANZSIC4..description) %>% tally %>% arrange(-n)
```

What is the count of unique trading names by geography:
```{r}
data_tr %>% 
  select(Trading.name,CLUE.small.area) %>% 
  unique() %>% 
  group_by(CLUE.small.area) %>% 
  tally %>% 
  arrange(-n)
```


From inspecting the raw data, initial data cleaning actions need to:

* Filter out `Vacant`, `Vacant Land` and `vacant` trading names (they are NULLs).
* If a business name has more than one ANZSIC, assign the highest counted ANZSIC to that business name




